---
title: "ICU Status Report"
author: "Abby Vogel"
date: "`r Sys.time()`"
format: html
editor: visual
---

```{r prep}
#| echo: false
#| warning: false
#| message: false

library(gt)
library(tidyverse)
library(data.table) ## For the fread function
library(lubridate)
library(googledrive)
library(googlesheets4)



source("sepsis_monitor_functions.R")

df <- makeSepsisDataset()

# We have to write the file to disk first, then upload it
df %>% write_csv("sepsis_data_temp.csv")

# Uploading happens here
sepsis_file <- drive_put(media = "sepsis_data_temp.csv", 
                         path = "https://drive.google.com/drive/folders/1qbUCGdFgUDzipeupj2iNQsEPHRKm732W",
                         name = "sepsis_data.csv")

# Set the file permissions so anyone can download this file.
sepsis_file %>% drive_share_anyone()



##pull in most recent data from google drive
## Calling drive_deauth() prevents R from trying to authenticate via a browser
## This is needed to make the GitHub Action work
drive_deauth()
file_link <- "https://drive.google.com/file/d/1JpH8Fw4SNsMyy_5IrkL7tOFfPreIfnw1/sepsis_data.csv"

## all data
drive_download(file_link, overwrite = TRUE)
all_data <- read.csv("sepsis_data.csv")

## All data up until now
new_data <- updateData(file_link)

## Include only most recent data
most_recent_data <- new_data %>%
  group_by(PatientID) %>%
  filter(obsTime == max(obsTime))

```

## Current Sepsis

A table listing the patients who currently have sepsis (if any), along with their most recent heart rate, temperature, and respiratory rate

```{r table1}
#| echo: false
#| message: false

table1_data <- most_recent_data %>%
  filter(SepsisLabel %in% 1) %>%
  select(1:5) %>%
  ungroup()

if(nrow(table1_data) != 0){
  gt(table1_data) %>%
    tab_header(title = "Current Patients with Sepsis") %>%
    cols_label(PatientID = "Patient ID",
               ICULOS = "ICU Length of Stay\n (Hours)",
               HR = "Heart Rate\n (BPM)",
               Temp = "Temperature\n (Deg F)",
               Resp = "Respiratory Rate\n (Breaths/Min)")
} else {
  print("No patients currently have sepsis.")
}
```

## Sepsis Patients' Medical History

Plots for all patients who have sepsis (if any) that show the complete history of their heart rate, temperature, and respiratory rate during their time in the ICU.

```{r}
#| echo: false
#| message: false
#| warning: false

plot_data <- all_data %>%
  filter(SepsisLabel %in% 1)

if(nrow(plot_data) != 0){
   ggplot(data = plot_data, aes(x = ICULOS, y = HR, group = as.factor(PatientID))) +
    geom_line(mapping = aes(color = as.factor(PatientID))) +
    guides(color = "legend") +
    labs(title = "Heart Rate History Through Length of Stay",
         y = "Heart Rate (BPM)",
         x = "Hours Since Admission to ICU",
         color = "Patient ID")

} else{
  print("No patients currently have sepsis.")
}


if(nrow(plot_data) != 0){
   
  ggplot(data = plot_data, aes(x = ICULOS, y = Temp, group = as.factor(PatientID)))+
    geom_line(mapping = aes(color = as.factor(PatientID))) +
    guides(color = "legend") +
    labs(title = "Temperature History Through Length of Stay",
         y = "Temperature (degrees Fahrenheit)",
         x = "Hours Since Admission to ICU",
         color = "Patient ID")  
}
    
if(nrow(plot_data) != 0){
    
  ggplot(data = plot_data, aes(x = ICULOS, y = Resp, group = as.factor(PatientID))) +
    geom_line(mapping = aes(color = as.factor(PatientID))) +
    guides(color = "legend") +
    labs(title = "Respiratory History Through Length of Stay",
         y = "Respriatory Rate (breaths per minute)",
         x = "Hours Since Admission to ICU",
         color = "Patient ID")
}
```

## Change in Medical Measurements for all Patients



```{r}
#| echo: false
#| message: false

table2 <- all_data %>%
  group_by(PatientID) %>%
  filter(obsTime == max(obsTime) | obsTime == max(obsTime[obsTime != max(obsTime)]))

table2_1 <- table2 %>%
  group_by(PatientID) %>%
  summarize("HR.change" = diff(HR, 1),"Temp.change" = diff(Temp, 1),  "Resp.change" =diff(Resp,1))

table2_gt <- gt(table2_1)

table2_gt %>%
  tab_header(title = "Most Recent Change in Vital Signs for All Patients") %>%
  cols_label(
    PatientID = "Patient ID",
    HR.change = "Change in\n Heart Rate",
    Temp.change = "Change in\n Temperature",
    Resp.change = "Change in\n Respiratory Rate"
  )
  
```
